Self Regulation Ontology Retest Analyses

### 2018-06-06 code/SRO_Retest_Analyses.Rmd
added lit ve emp measure plot

### Overlapping survery questions

@@

@@

Another way might be to compute confidence intervals using SEMs as described in the second half of Weir (2005) and check what percent of participants have scores that fall out of this range. I haven't pursued this for now.

Here we ask: Which variables have significant time effects in more than 5% of the bootstrapped samples?

@@

Are they predominantly in one or the other direction and does that differ depending on survey vs task?

@@

ADD!!!!

>>>>

### Overlapping survey questions

@@

for(i in 1:length(names(test_data))){
  if(is.numeric(test_data[,i]) & names(test_data)[i] %in% names(retest_data)){
    numeric_cols <- c(numeric_cols, names(test_data)[i])
  }
}
#Create df of point estimate reliabilities
rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
                     icc = rep(NA, length(numeric_cols)),
                     pearson = rep(NA, length(numeric_cols)),
                     partial_eta_sq = rep(NA, length(numeric_cols)),
                     sem = rep(NA, length(numeric_cols)),
                     var_subs = rep(NA, length(numeric_cols)),
                     var_ind = rep(NA, length(numeric_cols)),
                     var_resid = rep(NA, length(numeric_cols)))

row.names(rel_df) <- numeric_cols

for(i in 1:length(numeric_cols)){
  rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i]) 
  rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
  rel_df[numeric_cols[i], 'pearson'] <- get_pearson(numeric_cols[i])
  rel_df[numeric_cols[i], 'partial_eta_sq'] <- get_partial_eta(numeric_cols[i])
  rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
  rel_df[numeric_cols[i], 'var_subs'] <- get_var_breakdown(numeric_cols[i])$subs
  rel_df[numeric_cols[i], 'var_ind'] <- get_var_breakdown(numeric_cols[i])$ind
  rel_df[numeric_cols[i], 'var_resid'] <- get_var_breakdown(numeric_cols[i])$resid
}

rel_df$dv = row.names(rel_df)
row.names(rel_df) = seq(1:nrow(rel_df))
rel_df$task = 'task'
rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
rel_df[grep('holt', rel_df$dv), 'task'] = "task"
rel_df = rel_df %>%
  select(dv, task, spearman, icc, pearson, partial_eta_sq, sem, var_subs, var_ind, var_resid)
# row.names(rel_df) = NULL

@@

Another way might be to compute confidence intervals using SEMs as described in the second half of Weir (2005) and check what percent of participants have scores that fall out of this range.

First we ask: Which variables have significant time effects in more than 5% of the bootstrapped samples?

@@

@@
